### 2013-07-10 tests_Mg.Rmd
Mg dataset

```{r, message = FALSE, tidy = FALSE, echo = F}
## knitr configuration: http://yihui.name/knitr/options#chunk_options
opts_chunk$set(comment = "", error= TRUE, warning = FALSE, message = FALSE,
               tidy = FALSE, cache = TRUE, echo = T,
               fig.width = 6, fig.height = 6)
```
Testing California Housing
========================================================

@@

filename <- "Cal-Housing/cal_housing"  # where is the data (under dataset folder)
filepath <- paste0("datasets/",filename)
my.data <- read.csv(filepath, header=FALSE)

@@

# my.data <- na.omit(my.data) # the dataset has some NAs

@@

save(report, file="Cal-Housing250.Rda") # recover with load("Cal-Housing250.Rda")

@@

write.table(df, "Cal-Housing250.txt")
# df <- read.table("Cal-Housing250.txt")

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("California Housing dataset")

@@

write.table(df, "lambda.errors.Housing.txt")

df <- read.table("lambda.errors.Housing.txt", header=TRUE)

@@

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("California Housing dataset")
##############################################
# Check fitness progress

>>>>

```{r, message = FALSE, tidy = FALSE, echo = F}
## knitr configuration: http://yihui.name/knitr/options#chunk_options
opts_chunk$set(comment = "", error= TRUE, warning = FALSE, message = FALSE,
               tidy = FALSE, cache = TRUE, echo = T,
               fig.width = 6, fig.height = 6)
```
Testing MG
========================================================

Ref:

Gary William Flake and Steve Lawrence. 
Efficient SVM regression training with SMO. 
Machine Learning, 46:271-290, 2002.

# of data: 1,385
# of features: 6

@@

filename <- "Mg/mg_scale"  # where is the data (under dataset folder)
filepath <- paste0("datasets/",filename)
my.data <- read.csv(filepath, header=FALSE)

@@

# my.data <- na.omit(my.data) # the dataset has some NAs
my.data <- my.data[,c(2:7,1)] # place y as the last column

@@

save(report, file="Mg250.Rda") # recover with load("Mg250.Rda")

@@

write.table(df, "Mg250.txt")
# df <- read.table("Mg250.txt")

@@

qplot(method,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("regression method") +
  ggtitle("Mg dataset")

@@

write.table(df, "lambda.errors.Mg.txt")

df <- read.table("lambda.errors.Mg.txt", header=TRUE)

@@

library(ggplot2)
qplot(lambda,error,data=df,geom=c("jitter","boxplot")) + 
  ylab("root-mean-square error") + 
  xlab("lambda value") +
 # coord_cartesian(ylim = c(0, 50))  +
  ggtitle("Mg250 dataset")
##############################################
# Check fitness progress
